Convolutional equivalent layer for gravity data processing

### 2019-11-29 manuscript/synthetic_data.tex
review application to field data

\section{Synthetic tests}

We simulated three sources whose horizontal projections are shown in Figure \ref{fig:synthetic_data} as black lines. 
These sources are a sphere with radius of $1\,000$ m with density contrast of 
$-0.5\, \mathrm{g/cm^3}$ and two rectangular prisms with density contrasts of $0.35\, \mathrm{g/cm^3}$ (upper-left prism) 
and $0.4\, \mathrm{g/cm^3}$ (upper-right prism). 
Figure \ref{fig:synthetic_data} shows the gravity disturbance (vertical component of gravitational attraction) 
produced by these sources. The synthetic data are contaminated with additive pseudo-random Gaussian 
noise with zero mean and standard deviation of $0.015$ mGal.
We created $10\,000$ observation points regularly spaced on a grid of $100 \times 100$, on a 
horizontal plane at $-100$ m, and set a grid of equivalent point masses, each one directly beneath each 
observation point, located at depth $300$ m.

Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a show the data fits 
obtained, respectively, by the fast equivalent-layer technique \citep{siqueira-etal2017} 
and by our method. The corresponding residuals (Figures \ref{fig:classic_fast_val}b 
and \ref{fig:bccb_fast_val}b), defined as the difference between the simulated (Figure \ref{fig:synthetic_data}) 
and predicted data (Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a), show means close to 
zero and standard deviations of $0.0144$ mGal, indicating that both methods produced virtually the same results.
This excellent agreement is confirmed by Figures \ref{fig:delta_comparison} and 
\ref{fig:delta_rho}. They show that there are virtually no differences between, respectively, 
the predicted data (Figures \ref{fig:classic_fast_val}b and \ref{fig:bccb_fast_val}b) and the 
estimated mass distributions within the equivalent layers (not shown) yielded by 
both methods.

@@

The continued gravity data obtained with both methods agree with the true ones (not shown).
The difference is that the computation time spent by our method is 
approximately $1\,500$ times faster than that of the fast-equivalent-layer 
technique \citep{siqueira-etal2017}.

>>>>

\section{Application to synthetic data}

We simulated three sources whose horizontal projections are shown in Figure \ref{fig:synthetic_data} as black lines. 
These sources are a sphere with radius of $1\,000$ m with density contrast of 
$-0.5\, \mathrm{g/cm^3}$ and two rectangular prisms with density contrasts of $0.35\, \mathrm{g/cm^3}$ (upper-left prism) 
and $0.4\, \mathrm{g/cm^3}$ (upper-right prism). 
Figure \ref{fig:synthetic_data} shows the gravity disturbance (vertical component of gravitational attraction) 
produced by these sources. The synthetic data are contaminated with additive pseudo-random Gaussian 
noise with zero mean and standard deviation of $0.015$ mGal.
We created $N = 10\,000$ observation points regularly spaced on a grid of $100 \times 100$, on a 
horizontal plane at $z_{1} = -100$ m, and set a grid of equivalent point masses, each one directly beneath each 
observation point, located at depth $z_{0} = 300$ m.

Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a show the data fits 
obtained, respectively, by the fast equivalent-layer technique \citep{siqueira-etal2017} 
and by our method. The corresponding residuals (Figures \ref{fig:classic_fast_val}b 
and \ref{fig:bccb_fast_val}b), defined as the difference between the simulated (Figure \ref{fig:synthetic_data}) 
and predicted data (Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a) after $N^{it} = XXXX$ iterations, 
show means close to zero and standard deviations of $0.0144$ mGal, indicating that both methods produced virtually 
the same results.
This excellent agreement is confirmed by Figures \ref{fig:delta_comparison} and 
\ref{fig:delta_rho}. They show that there are virtually no differences between, respectively, 
the predicted data (Figures \ref{fig:classic_fast_val}b and \ref{fig:bccb_fast_val}b) and the 
estimated mass distributions within the equivalent layers (not shown) yielded by 
both methods.

@@

The continued gravity data obtained with both methods agree with the true ones (not shown).
The difference is that the computation time spent by our method is 
approximately $1\,500$ times smaller than that of the fast-equivalent-layer 
technique \citep{siqueira-etal2017}.
